`r paste(params$file_path, ' ', params$intervention, ' Handover Plots')`

### 2023-12-15 minos/validation/handovers.Rmd

---
title: "MINOS Handover Plots"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: true
    df_print: paged
    code_folding: hide
---

@@

```{r}
# Read raw datafiles in
raw.files <- list.files(here::here('data', 'final_US'), pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
raw.dat <- do.call(rbind, lapply(raw.files, read.csv))

out.path <- here::here('output', 'default_config/')
base.dat <- read_singular_local_out(out.path, 'baseline', drop.dead = TRUE)
```

@@

```{r}
base.child.ages <- base.dat %>%
  dplyr::select(pidp, hidp, time, "child_ages", "nkids") %>%
  filter(time > 2009) %>%
  group_by(time, hidp) %>%
  summarise(child_ages = find_mode(child_ages))

s<- strsplit(base.child.ages$child_ages, "_")

base.child.ages.expanded <- data.frame(time = rep(base.child.ages$time, sapply(s, length)), expanded_child_ages = unlist(s))
base.child.ages.expanded <- base.child.ages.expanded %>%
  group_by(time, expanded_child_ages) %>%
  summarise(age_counts = n())

ggplot(data = base.child.ages.expanded, mapping = aes(x = time, y = age_counts, group = expanded_child_ages, colour =  factor(as.numeric(expanded_child_ages)))) +
  geom_line() +
  labs(title = "Child Age Counts Over Time", subtitle = 'Counts by Level') +
  scale_colour_viridis_d() +
  xlab('Year') +
  ylab('Count')

ggplot(data = base.child.ages.expanded, mapping = aes(x = factor(as.numeric(expanded_child_ages)), y = age_counts, group = factor(time), colour = factor(time))) +
  geom_line() +
  labs(title = "Child Age Counts Over Time", subtitle = 'Counts by Level') +
  scale_colour_viridis_d() +
  xlab('Year') +
  ylab('Count')

base.child.ages.nkids <- base.dat %>%
  group_by(time, hidp) %>%
  summarise(nkids_counts = mean(nkids)) %>%
  group_by(time) %>%
  summarise(nkids_by_year = sum(nkids_counts))

ggplot(data = base.child.ages.nkids, mapping = aes(x = time, y = nkids_by_year)) +
  geom_line() +
  labs(title = "nkids Count Over Time", subtitle = 'Counts by Level') +
  xlab('Year') +
  ylab('Count')

@@

>>>>

---
params:
    file_path: '' # default arguments. specify others in command line.
    intervention: ''
title: "`r paste(params$file_path, ' ', params$intervention, ' Handover Plots')`"
output:
  #output_file: "`r paste('minos/validation/', params$file_path, '_', params$intervention, '_handovers.html') `"
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: true
    df_print: paged
    code_folding: hide

---

@@

```{r}

file_path <- params$file_path
intervention <- params$intervention

# Read raw datafiles in
raw.files <- list.files(here::here('data', 'final_US'), pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
raw.dat <- do.call(rbind, lapply(raw.files, read.csv))

#out.path <- here::here('output', 'default_config/')
#base.dat <- read_singular_local_out(out.path, 'baseline', drop.dead = TRUE)

out.path <- here::here('output', file_path)
base.dat <- read_singular_local_out(out.path, intervention, drop.dead = TRUE)
```

@@

```{r}
raw.child.ages <- raw.dat %>%
  dplyr::select(pidp, hidp, time, "child_ages", "nkids") %>%
  filter(time > 2013) %>%
  group_by(time, hidp) %>%
  summarise(child_ages = find_mode(child_ages))

r.s<- strsplit(raw.child.ages$child_ages, "_")

raw.child.ages.expanded <- data.frame(time = rep(raw.child.ages$time, sapply(r.s, length)), expanded_child_ages = unlist(r.s))
raw.child.ages.expanded <- raw.child.ages.expanded %>%
  group_by(time, expanded_child_ages) %>%
  summarise(age_counts = n()) %>%
  mutate(source = 'final_US') %>%
  filter(expanded_child_ages <= 16)

base.child.ages <- base.dat %>%
  dplyr::select(pidp, hidp, time, "child_ages", "nkids") %>%
  filter(time > 2009) %>%
  group_by(time, hidp) %>%
  summarise(child_ages = find_mode(child_ages))

b.s<- strsplit(base.child.ages$child_ages, "_")

base.child.ages.expanded <- data.frame(time = rep(base.child.ages$time, sapply(b.s, length)), expanded_child_ages = unlist(b.s))
base.child.ages.expanded <- base.child.ages.expanded %>%
  group_by(time, expanded_child_ages) %>%
  summarise(age_counts = n()) %>%
  mutate(source = 'baseline')

combined <- rbind(raw.child.ages.expanded, base.child.ages.expanded)

ggplot(data = combined, mapping = aes(x = time, y = age_counts, group = expanded_child_ages, colour =  factor(as.numeric(expanded_child_ages)))) +
  geom_line() +
  geom_vline(xintercept = start.year) +
  labs(title = "Child Age Counts Over Time", subtitle = 'Counts by Level') +
  scale_colour_viridis_d() +
  xlab('Year') +
  ylab('Count')

ggplot(data = combined, mapping = aes(x = factor(as.numeric(expanded_child_ages)), y = age_counts, group = factor(time), colour = factor(time))) +
  geom_line() +
  geom_vline(xintercept = start.year) +
  labs(title = "Child Age Counts Over Time", subtitle = 'Counts by Level') +
  scale_colour_viridis_d() +
  xlab('Year') +
  ylab('Count')

base.child.ages.nkids <- base.dat %>%
  group_by(time, hidp) %>%
  summarise(nkids_counts = mean(nkids)) %>%
  group_by(time) %>%
  summarise(nkids_by_year = sum(nkids_counts)) %>%
  mutate(source = 'baseline')

raw.child.ages.nkids <- raw.dat %>%
  group_by(time, hidp) %>%
  summarise(nkids_counts = mean(nkids)) %>%
  group_by(time) %>%
  summarise(nkids_by_year = sum(nkids_counts)) %>%
  mutate(source = 'final_US')

combined.nkids <- rbind(base.child.ages.nkids, raw.child.ages.nkids)

ggplot(data = combined.nkids, mapping = aes(x = time, y = nkids_by_year, group = source, colour = source)) +
  geom_line() +
  labs(title = "nkids Count Over Time", subtitle = 'Counts by Level') +
  xlab('Year') +
  ylab('Count')

@@

```{r}
